Viscous Erosion in Porous Media

### 2018-03-20 docs/methods/erosion_methods.tex
NM

To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations. Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting form. To circumvent this problem, we modify the normal velocity $\Vn$ to have zero mean,
\begin{align}
\Vn \leftarrow \Vn - \mean{\Vn} \, .
\end{align}
This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.

>>>>

To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations. Section \ref{sec:scaling}, however, shows that the magnitude of the shear stress diverges as the body vanishes, which causes our simulations lose accuracy just in the final critical moments when the body is expected to approach its limiting shape. To circumvent this problem, we remove the effect of shrinking by forcing $\Vn$ to have zero mean,
\begin{align}
\Vn \leftarrow \Vn - \mean{\Vn} \, .
\end{align}
This modification allows erosion to sculpt the shape as it would normally, but with the area artificially held fixed.
